Characterisation of MSC in clinical trial reports: analysis of published descriptors

### 2020-04-27 paper2_figures.Rmd
draft

# Figures specification
* titled
* cited in numerical order in the text using Arabic numbers. 
* no additional charges for color. 
* submitted as individual files
* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
* Figures may be submitted as multipart panels.
*  *.tif* or .eps 
* final publication size; 1-column width or, if necessary, 1½ column width. The * 2-column width should not be used unless necessary.
* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
* Calibri font sub sans serif Arial
* Multipanel labeled using uppercase 12-point Calibri Bold. 
* minimum text size of 6 points
* bold enough to be easily read after reduction, as should all symbols used in the * figure. Line or bar graphs or flow charts with text should be created in black and * white, not shades of gray, which are difficult to reproduce in even tones. If more * than two sets of data are represented, use of fill patterns or colors (not gray) is * suggested to present the data clearly.
* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for * combination halftones, and 1000 dpi for line art.

```{r pkg}
library(tidyverse)
library(RColorBrewer)
library(readxl)
library(kableExtra)
library(tiff)
library(grid)
library(patchwork)

@@

# figure saving settings
units = "in"
fig_w <- 3.2
fig_w_1.5 <- 4.5
fig_w_2 <- 5.8
fig_h <- 4.5
fig_h_1.5 <- 4.5 * 1.5
dpi <- 300
device <- "tiff"

@@

```{r import}
# file <- here::here("data", "Checked Data.xlsx")
# 
# # added a row for column names more useful
# # # skipped first two rows of of old col names
# 
# dat <- read_excel(file, sheet = "Checked Data")

@@

```{r tidy-data}
# recode country so those with one paper are
# "Other"
# dat <- dat %>%
#   mutate(Country2 = recode_factor(Country,
#                                 Brazil = "Brazil",
#                                 China = "China",
#                                 Denmark = "Denmark",
#                                 Egypt = "Egypt",
#                                 India = "India",
#                                 Japan = "Japan",
#                                 Korea = "Korea",
#                                 Netherlands = "Netherlands",
#                                 Poland = "Poland",
#                                 `Rep Korea` = "Rep Korea",
#                                 Russia = "Russia",
#                                 Spain = "Spain",
#                                 Taiwan = "Taiwan",
#                                 USA = "USA",
#                                 .default = "Other"))
```

```{r}
# dat <- dat %>%
#   mutate(Phase_condensed = recode_factor(Phase,
#                                I = "I",
#                                `I/IIa` = "I",
#                                `I/II` = "I",
#                                 II = "II",
#                                 IIa = "II",
#                                IIb = "II",
#                                III = "III"))
```

```{r}
# dat <- dat %>%
#   mutate(test_results = recode_factor(`Test Results?`,
#                                        n = "Average value (n)",
#                                        s = "Stated as 'standard phenotype' (s)",
#                                        o = "Not discussed (o)",
#                                        y = "Phenotypic markers reported (y)",
#                                        t = "Tests done but not reported (t)"))
# dat$test_results <- fct_relevel(dat$test_results,
#                               "Phenotypic markers reported (y)", 
#                               "Average value (n)",
#                               "Tests done but not reported (t)",
#                               "Stated as 'standard phenotype' (s)",
#                               "Not discussed (o)")
```

```{r}
# MOA - recode NS to Not stated
# dat <- dat %>%
#   mutate(MOA = recode_factor(MOA,
#                              NS = "Not stated",
#                              paracrine = "Paracrine",
#                              immune = "Immune",
#                              differentiation = "Differentiation",
#                              multi = "Multiple"))
# 
# dat$MOA <- fct_relevel(dat$MOA,
#                        "Paracrine",
#                        "Immune",
#                        "Differentiation",
#                        "Multiple",
#                        "Not stated")
```

```{r}
# recode stem/stromal
# dat <- dat %>%
#   mutate(stem_stromal = recode_factor(`Stem/Stromal`,
#                              `multipotent stromal` = "Multipotent Stromal",
#                              regenerative = "Regenerative",
#                              stem = "Stem",
#                              stromal = "Stromal"))
# 
# dat$stem_stromal <- fct_relevel(dat$stem_stromal,
#                                 "Stromal",
#                                 "Stem",
#                                 "Multipotent Stromal",
#                                 "Regenerative")
# note: no longer an 'other' category, new regerative category
```

# # Recode O, A and C into the 5 categories that appar 
# dat <- dat %>%
#   mutate(differentiation = ifelse(O == "y" &
#                             A == "y" &
#                             C == "y",
#                           "Demonstrated tripotency",
#                           ifelse(O == "n" &
#                                    A == "n" &
#                                    C == "n",
#                                  "Not Stated",
#                                  ifelse(O == "y" &
#                                           A == "y" &
#                                           C == "n",
#                                         "Demonstrated bipotency (OA)",
#                                         ifelse(O == "y" &
#                                                  A == "n" &
#                                                  C == "n",
#                                                "Demonstrated potency (O)",
#                                                ifelse(O == "m"
#                                                       & A == "m" &
#                                                         C == "n",
#                                                       "Claimed bipotency (OA)",
#                                                       ifelse(O == "m" &
#                                                                A == "m" &
#                                                                C == "m",
#                                                              "Claimed tripotency", NA)))))))        
# 
# dat$differentiation <- fct_relevel(dat$differentiation,
#                                 "Demonstrated tripotency",
#                                 "Demonstrated bipotency (OA)",
#                                 "Demonstrated potency (O)",
#                                 "Claimed tripotency",
#                                 "Claimed bipotency (OA)",
#                                 "Not Stated")                        
```

```{r}
# Recode O, A and C into 2 categories, all n = No, anything else = Yes 
# dat <- dat %>%
#   mutate(differentiation2 = ifelse(O == "n" &
#                                    A == "n" &
#                                    C == "n",
#                                  "No", "Yes"))      
# 
# dat$differentiation2<- fct_relevel(dat$differentiation2,
#                                 "No","Yes")                        
```
## write to file
```{r}
# file <- "data/checked_processed.csv"
# write_csv(dat, file)
```

```{r}
file <- "data/checked_processed_aw_corrections.csv"
dat <- read_csv(file)
```

```{r}
dat <- dat %>%
  mutate(test_results = recode_factor(`Test Results?`,
                                       n = "Average value (n)",
                                       s = "Stated as 'standard phenotype' (s)",
                                       o = "Not discussed (o)",
                                       y = "Phenotypic markers reported (y)",
                                       t = "Tests done but not reported (t)"))
dat$test_results <- fct_relevel(dat$test_results,
                              "Phenotypic markers reported (y)",
                              "Average value (n)",
                              "Tests done but not reported (t)",
                              "Stated as 'standard phenotype' (s)",
                              "Not discussed (o)")
```

```{r}
# add a count of the number of markers tested for "Average value (n)". select columns like _test
test_cols <- names(select(dat, ends_with("_test")) )
dat <- dat %>%
  mutate(marker_count = rowSums(.[test_cols] == "p"))

dat %>% group_by(MOA) %>% summarise(n = length(MOA))

dat$MOA <- fct_relevel(dat$MOA,
                       "Paracrine",
                       "Immune",
                       "Differentiation",
                       "Multiple",
                       "Not stated")
```

```{r}
dat %>% group_by(stem_stromal) %>% summarise(n = length(stem_stromal))

dat$stem_stromal <- fct_relevel(dat$stem_stromal,
                                "Stromal",
                                "Stem",
                                "Multipotent Stromal",
                                "Regenerative")
```

```{r}
# cd values for

# note: file had missing value for Phas, this was looked up in "Meta-Analysis Data Collection.xlsx"
# as phase I/IIa
# note: ref 55, patient 6, marker CD45+/CD105+ contained value ND - I assumed this was no data.
# note - I have assumed range  is mean +/- se (not sd)
# file <- here::here("data", "Paper 2 - Charts for Emma.xlsx")
# cd_dat <- read_excel(file, sheet = "cd_values_single")
# cd_dat2 <- read_excel(file, sheet = "cd_values_range")
```

```{r tidy-cd-data}
# cd_dat <- cd_dat %>% 
#   gather(key = marker, value = value, -Ref, -Phase, -patient, -notes)
# cd_dat$value <- as.numeric(cd_dat$value)
# 
# cd_dat2 <- cd_dat2 %>% 
#   gather(key = marker, value = value, -Ref, -Phase, -n)
# 
# for (i in 1:length(cd_dat2$value)) {
#   temp <- strsplit(cd_dat2$value[i], split = "\\s.\\s") %>% unlist()
#   cd_dat2$mean_value[i] <- as.numeric(temp[1])
#   cd_dat2$se_value[i] <- as.numeric(temp[2])
# }
# cd_dat2 <- cd_dat2 %>% 
#   filter(!is.na(value)) %>% 
#   select(Ref, marker, mean_value, n, se_value, -Phase, -value)

```{r}
dat %>% group_by(O) %>% 
  summarise(n = length(O), pc = n/84)
```
```{r}
dat %>% group_by(A) %>% 
  summarise(n = length(A), pc = n/84)
```
```{r}
dat %>% group_by(C) %>% 
  summarise(n = length(C), pc = n/84)
```
```{r}
dat %>% group_by(differentiation) %>% 
  summarise(n = length(differentiation), pc = n/84)
```

```{r}
dat %>% group_by(other_functionality) %>% 
  summarise(n = length(other_functionality), pc = n/84)
```
# Figures

@@

orig$step_names <- fct_relevel(orig$step_names,
                               "mesenchymal",
                               "article",
                               "cell tissue etc",
                               "clinical etc",
                               "not biotech etc",
                               "exc conf etc")

@@

```{r fig1}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 2,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = rev(pal))

@@

```{r country-prep}
summary_country <- dat %>%
  group_by(Country) %>% 
  summarise(n = length(Country))

@@

```{r fig3-country-bar}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(Country, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3],
           size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 6, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 6, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

@@

summary_phase <- dat %>%
  group_by(Phase) %>% 
  summarise(n = length(Phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))
summary_phase <- summary_phase %>%
  mutate(Phase_condensed = recode_factor(Phase,
                               I = "I",
                               `I/IIa` = "I",
                               `I/II` = "I",
                                II = "II",
                                IIa = "II",
                               IIb = "II",
                               III = "III",
                               NS = "NS"))

summary_phase_condensed <- dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

@@

```{r fig4-phase}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(Phase,n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3], size = 0) +
  xlab("") +
  geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 1),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

### Three phase

```{r fig4-phase-3}
# phase_3_bar <- summary_phase_condensed %>% 
#   ggplot(aes(x = reorder(Phase_condensed, n), y = n)) +
#   geom_bar(stat = "identity", fill = pal[3],size = 0) +
#   xlab("") +
#   geom_text(aes(y = n + 6, label = pc) ) +
#   scale_y_continuous(name = "Number of Articles", 
#                      breaks = seq(0, 65, 5),
#                      minor_breaks = seq(0, 65, 1),
#                      limits = c(0, 65),
#                      expand = c(0, 0)) +
#   scale_x_discrete(expand = c(0, 0)) +
#   labs(title = "Wilson, Alison, Figure 4. TOP" ) +
#   theme_classic() +
#   theme(axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 8, colour = "black"),
#         axis.ticks.y = element_blank(),
#         axis.text.y  = element_text(size = 8, colour = "black"),
#         panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         plot.title = element_text(hjust = 0, size = 4)) +
#   coord_flip()
# 
# ggsave("figs/fig_4_Article_phase_3.tif", 
#        plot = phase_3_bar, 
#        device = device,
#        width = fig_w, 
#        height = fig_w,
#        units = units,
#        dpi = dpi)

@@

```{r source_year_prep}
summary_tissue <- dat %>% 
  group_by(Source, Year = factor(Year), 
           .drop = FALSE) %>% 
  summarise(n = length(Source))
dat %>% 
  group_by(Source, 
           .drop = FALSE) %>% 
  summarise(n =length(Source), pc = n/84)

### stacked
```{r fig5-source-year-stack}
source_year <- summary_tissue %>% 
  ggplot(aes(x = Year, y = n, fill = Source)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal[c(1,3,5,6)],
                    guide = guide_legend(nrow = 3, title = NULL )) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 20, 2),
                    minor_breaks = seq(0, 20, 2),
                    limits = c(0, 20),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = c(0.2, 0.9),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))

@@

```{r test-quality-prep}
summary_test <- dat %>% 
  group_by(test_results) %>% 
  summarise(n = length(test_results),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

@@

```{r testquality}
test_bar <- summary_test %>% 
  ggplot(aes(x = reorder(test_results, n), y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  xlab("") +
  geom_text(aes(y = n + 6, label = pc) ) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 50, 5),
                     minor_breaks = seq(0, 50, 1),
                     limits = c(0, 50),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0),
                   labels = c("Stated as 'standard\nphenotype' (s)",
                              "Phenotypic markers\nreported (y)",
                              "Tests done but\nnot reported (t)",
                              "Not discussed (o)",
                              "Average value (n)")) +
  labs(subtitle = "A") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4),
        plot.margin = margin(r = 0.1, b = 0.1, l = 0, unit="in")) +
  coord_flip()

@@

### panel 2 how many markers had average values  
```{r}
summary_marker_count <- dat %>% 
  filter(test_results == "Average value (n)") %>%
  group_by(marker_count) %>% 
  summarise(n = length(marker_count))

@@

dat %>%
  group_by(Phase_condensed) %>% 
  summarise(n = length(Phase_condensed),
            pc = n/84)

summary_phase_test <- dat %>%
  group_by(Phase_condensed, test_results) %>% 
  summarise(n = length(Phase_condensed))
```

```{r phasetest}
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = Phase_condensed, y = n, fill = test_results)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
 labs(subtitle = "C") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 8),
        legend.position = "none", 
        plot.margin = margin(r = 0.3, l = 0.1, t = 0, unit="in"))

### Stacked by percent of article

```{r fig7-phase-test-pc}
# phase_test2 <- summary_phase_test %>% 
#   ggplot(aes(x = Phase_condensed, y = n)) +
#   geom_bar(aes(fill = test_results), 
#            stat = "identity", 
#            size = 0, 
#            position = "fill") +
#   scale_fill_manual(values = pal,
#                     name = "Test results") +
#   scale_y_continuous(name = "Proportion of Articles",
#                      breaks = seq(0, 1, 0.2),
#                 #     limits = c(0, 1.2),
#                      expand = c(0, 0)) +
#   scale_x_discrete(expand = c(0, 0), name = "Phase") +
#   geom_text(data = summary_phase_condensed,
#             aes(x = Phase_condensed, y = 1.05, vjust = 1,
#                 label = paste("n = ",n)),size=3) +
#  labs(subtitle = "B") +
#   theme_classic() +
#   theme(axis.text.x = element_text(size = 8, colour = "black"),
#         axis.text.y  = element_text(size = 8, colour = "black"),
#         panel.grid.major.x = element_blank(),
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         #  plot.title = element_text(hjust = 0, size = 8),
#         legend.position = "none",
#         plot.margin = margin(r = 0, l = 0, unit="in"))

@@

layout <- "
aaaaaaa#
aaaaaaa#
aaaaaaa#
#bbbbccc
#bbbbccc
#bbbbccc
#bbbbccc
#bbbbccc
"

@@

```{r}
dat
```

@@

# select the test columns and count the number of articles for each marker and category
test_cols

charact_by_marker_ref <- dat %>% 
  select(ends_with("_test"), `Ref #`) %>% 
  pivot_longer(cols = -`Ref #`, names_to = "marker", values_to = "status")

@@

charact_by_marker_ref <- charact_by_marker_ref %>% 
  mutate(marker2 = str_replace(marker, "_test", ""))

# change levels of status and markers.
# markers
# process test_col names
test_cols <- str_replace(test_cols, "_test", "")
# set the levels in that order
charact_by_marker_ref$marker2 <- factor(charact_by_marker_ref$marker2, levels = test_cols)

# status
# recode status
charact_by_marker_ref <- charact_by_marker_ref %>%
  mutate(test_status = recode_factor(status,
                             p = "Performed, value reported",
                             m = "Performed, no value reported",
                             n = "Not mentioned"))

charact_by_marker_ref$test_status <- fct_relevel(charact_by_marker_ref$test_status,
                                                     "Not mentioned",
                                                     "Performed, no value reported",
                                                     "Performed, value reported")

charact_by_marker_summary <- charact_by_marker_ref %>% 
  group_by(marker2, test_status) %>% 
  summarise(n = length(marker2))

@@

# Figure 8
```{r}
functionality <- dat %>% 
  select(O, A, C, other_functionality) %>% 
  pivot_longer(cols = everything(), names_to = "Functionality", values_to = "status") %>% 
  group_by(Functionality, status) %>% 
  summarise(n = length(status))

@@

functionality$status <- fct_relevel(functionality$status,
                                    "Not mentioned",
                                    "Mentioned",
                                    "Performed")

# recode functionality
functionality <- functionality %>%
  mutate(potency_ass = recode_factor(Functionality,
                                     other_functionality = "Other functionality",
                                     C = "Chondrogenesis",
                                     A = "Adipogenesis",
                                     O = "Osteogenesis"))

functionality$potency_ass <- fct_relevel(functionality$potency_ass,
                                         "Other functionality",
                                         "Chondrogenesis",
                                         "Adipogenesis",
                                         "Osteogenesis")

@@

>>>>

# Figures specification
* titled
* cited in numerical order in the text using Arabic numbers. 
* no additional charges for color. 
* submitted as individual files
* labeled with the Corresponding Author name, the appropriate figure number, and  orientation (e.g., “top”)
* Figures may be submitted as multipart panels.
*  *.tif* or .eps 
* final publication size; 1-column width or, if necessary, 1½ column width. The  2-column width should not be used unless necessary.
* 1.0 column = 3.2 Inches, 8.2 Centimeters, 19.25 Picas
* 1.5 column = 4.5 Inches, 11.4 Centimeters, 27.00 Picas
* 2.0 column = 5.8 Inches, 14.8 Centimeters, 35.00 Picas
* height of all figures <= to 9.6inches / 24.5 cm / 58 picas.
* Calibri font sub sans serif Arial
* Multipanel labeled using uppercase 12-point Calibri Bold. 
* minimum text size of 6 points
* bold enough to be easily read after reduction, as should all symbols used in the * figure. Line or bar graphs or flow charts with text should be created in black and white, not shades of gray, which are difficult to reproduce in even tones. If more than two sets of data are represented, use of fill patterns or colors (not gray) is suggested to present the data clearly.
* Minimum resolution is 300 dpi for color and grayscale figures, 600 dpi for  combination halftones, and 1000 dpi for line art.

```{r pkg}
library(tidyverse)
# library(readxl)
# library(kableExtra)
library(tiff)
library(grid)
library(patchwork)
library(janitor)

@@

# figure saving settings
units = "in"
fig_w <- 3.2
fig_w_1.5 <- 4.5
fig_w_2 <- 5.8
fig_h <- 4.5
fig_h_1.5 <- 4.5 * 1.5
dpi <- 600
device <- "tiff"

@@

## write to file
```{r}
# file <- "data/checked_processed_aw_corrections.csv"
# write_csv(dat, file)
```

```{r}
file <- "data/checked_processed_aw_corrections.csv"
dat <- read_csv(file)
# write(names(dat), "data/varnames.txt")

@@

```{r}
# put levels in
source("levels.R")
```

# Figures

@@

@@

```{r fig1}
article_funnel <- to_poly_orig %>%
  ggplot() +
  geom_polygon(aes(x,
                   y,
                   group = group,
                   fill = step_names),
               size = 0) +
  geom_label(aes(x = 0,
                y = y,
                label = n),
            data = labels, 
            size = 3,
            label.size = 0,
            label.padding = unit(0.1, "lines"),
            label.r = unit(0.1, "lines")) +
  scale_y_continuous(breaks = labels$y,
                     labels = labels$step_names2) +
  labs(title = "Wilson, Alison, Figure 1. TOP" ) +
  theme_minimal() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y  = element_text(size = 7, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
    scale_fill_manual(values = rev(pal))

@@

```{r country-prep}
summary_country <- dat %>%
  group_by(country) %>% 
  summarise(n = length(country))

@@

```{r fig3-country-bar}
country_bar <- summary_country %>% 
  ggplot(aes(x = reorder(country, n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3],
           size = 0) +
  xlab("") +
  scale_y_continuous(name = "Number of articles", 
                     breaks = seq(0, 16, 1),
                     minor_breaks = seq(0, 16, 1),
                     limits = c(0, 16),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 3. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 7, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()
ggsave("figs/fig_3_Article_country.tif", 
       plot = country_bar, 
       device = device,
       width = fig_w, 
       height = fig_w,
       units = units,
       dpi = dpi)

@@

summary_phase <- dat %>%
  group_by(phase) %>% 
  summarise(n = length(phase),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

summary_phase_condensed <- dat %>%
  group_by(phase_condensed) %>% 
  summarise(n = length(phase_condensed),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

@@

```{r fig4-phase}
phase_bar <- summary_phase %>% 
  ggplot(aes(x = reorder(phase,n), y = n)) +
  geom_bar(stat = "identity", fill = pal[3], size = 0) +
  xlab("") +
  geom_text(aes(y = n + 4, label = pc) ) +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 45, 5),
                     minor_breaks = seq(0, 45, 1),
                     limits = c(0, 45),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  labs(title = "Wilson, Alison, Figure 4. TOP" ) +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4)) +
  coord_flip()

@@

```{r source_year_prep}
summary_tissue <- dat %>% 
  group_by(source, year, 
           .drop = FALSE) %>% 
  summarise(n = length(source))
dat %>% 
  group_by(source, 
           .drop = FALSE) %>% 
  summarise(n =length(source), pc = n/84)

@@

### stacked
```{r fig5-source-year-stack}
source_year <- summary_tissue %>% 
  ggplot(aes(x = year, y = n, fill = source)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal[c(1,3,5,6)],
                    guide = guide_legend(nrow = 3, title = NULL )) +
  scale_y_continuous(name = "Number of Articles",
                    breaks = seq(0, 20, 2),
                    minor_breaks = seq(0, 20, 2),
                    limits = c(0, 20),
                    expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Year") +
  labs(title = "Wilson, Alison, Figure 5. TOP" ) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 4),
        legend.position = c(0.2, 0.9),
        legend.text = element_text(size = 6, colour = "black"),
        legend.key.size = unit(0.2, "in"))

@@

```{r test-quality-prep}
summary_test <- dat %>% 
  group_by(test_results_2) %>% 
  summarise(n = length(test_results_2),
            pc = paste0(round(100 * n / 84, 1 ), "%"))

@@

```{r testquality}
test_bar <- summary_test %>% 
  ggplot(aes(x = reorder(test_results_2, n), y = n, fill = test_results_2)) +
  geom_bar(stat = "identity", size = 0) +
  xlab("") +
  geom_text(aes(y = n + 6, label = pc) ) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles", 
                     breaks = seq(0, 50, 5),
                     minor_breaks = seq(0, 50, 1),
                     limits = c(0, 50),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0),
                   labels = c("Stated as 'standard\nphenotype' (s)",
                              "Phenotypic markers\nreported (y)",
                              "Tests done but\nnot reported (t)",
                              "Not discussed (o)",
                              "Average value (n)")) +
  labs(subtitle = "A") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(size = 8, colour = "black"),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.position = "none",
        plot.title = element_text(hjust = 0, size = 4),
        plot.margin = margin(r = 0.1, b = 0.1, l = 0, unit="in")) +
  coord_flip()

@@

### panel 2 how many markers had average values  
```{r}
dat %>% 
  filter(test_results_2 != "Average value (n)") %>%
  filter(marker_count == 1) %>% 
  select(ref_number,test_results_2, test_results)

summary_marker_count <- dat %>% 
  filter(test_results_2 == "Average value (n)") %>%
  group_by(marker_count) %>% 
  summarise(n = length(marker_count))

@@

dat %>%
  group_by(phase_condensed) %>% 
  summarise(n = length(phase_condensed),
            pc = n/84)

summary_phase_test <- dat %>%
  group_by(phase_condensed, test_results_2) %>% 
  summarise(n = length(phase_condensed))
```

```{r phasetest}
phase_test <- summary_phase_test %>% 
  ggplot(aes(x = phase_condensed, y = n, fill = test_results_2)) +
  geom_bar(stat = "identity", size = 0) +
  scale_fill_manual(values = pal,
                    name = "Test results") +
  scale_y_continuous(name = "Number of Articles",
                     breaks = seq(0, 55, 10),
                     minor_breaks = seq(0, 55, 5),
                     limits = c(0, 55),
                     expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), name = "Phase") +
 labs(subtitle = "C") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 8, colour = "black"),
        axis.text.y  = element_text(size = 8, colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(hjust = 0, size = 8),
        legend.position = "none", 
        plot.margin = margin(r = 0.3, l = 0.1, t = 0, unit="in"))

@@

layout <- "
aa
bc
"

@@

@@

# select the test columns and count the number of articles for each marker and category
test_cols <- names(select(dat, ends_with("_test")))

test_by_attribute <- dat %>% 
  select(test_cols, ref_number) %>% 
  pivot_longer(cols = -ref_number, 
               names_to = "marker", 
               values_to = "status")

@@

test_by_attribute <- test_by_attribute %>% 
  mutate(marker2 = str_replace(marker, "_test", ""))

# change levels of status and markers.
# markers
# process test_col names
test_cols <- str_replace(test_cols, "_test", "")
# set the levels in that order
test_by_attribute$marker2 <- factor(charact_by_marker_ref$marker2, 
                                    levels = test_cols)

# status
# recode status
test_by_attribute <- test_by_attribute %>%
  mutate(test_status = recode_factor(status,
                                     p = "Performed, value reported",
                                     m = "Performed, no value reported",
                                     n = "Not mentioned"))

test_by_attribute$test_status <- fct_relevel(test_by_attribute$test_status,
                                             "Not mentioned",
                                             "Performed, no value reported",
                                             "Performed, value reported")

test_by_attribute_summary <- test_by_attribute %>% 
  group_by(marker2, test_status) %>% 
  summarise(n = length(marker2))

@@

# Figure 8
```{r}
functionality <- dat %>% 
  select(O, A, C, other_functionality) %>% 
  pivot_longer(cols = everything(), names_to = "type", values_to = "status") %>% 
  group_by(type, status) %>% 
  summarise(n = length(status)) %>% 
  ungroup(type, status)

@@

functionality$status <- fct_relevel(functionality$status,
                                    "Not mentioned",
                                    "Mentioned",
                                    "Performed")
levels(functionality$status)

# recode functionality
functionality <- functionality %>%
  mutate(type = recode_factor(type,
                              other_functionality = "Other functionality",
                              C = "Chondrogenesis",
                              A = "Adipogenesis",
                              O = "Osteogenesis"))

functionality$type <- fct_relevel(functionality$type,
                                         "Other functionality",
                                         "Chondrogenesis",
                                         "Adipogenesis",
                                         "Osteogenesis")

@@

# disease targets
dat %>% group_by(Indication) %>% 
  summarise(n = length(Indication)) %>% 
  ggplot(aes(x = Indication, y = n)) +
  geom_bar(stat="identity")
